### 2012-07-30 inst/examples/bias_table.Rmd
bias table with measurement error, for issue #17

`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
````

@@

``` {r noise}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r othernoise}
z_m <- function() 1
z_i <- function() 1
````

@@

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat1 <- determine_SDP_matrix(f, pars1, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  }
SDP_Mat2 <- determine_SDP_matrix(f, pars2, x_grid, h_grid, sigma_g, pdfn)
````

@@

``` {r  }
SDP_Mat3 <- determine_SDP_matrix(f, pars3, x_grid, h_grid, sigma_g, pdfn)
````

>>>>

`ro cache=FALSE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table_measurement/", verbose=TRUE or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .01
sigma_m <- .5
````

@@

``` {r noise}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
````

@@

``` {r othernoise}
z_i <- function() 1
````

@@

``` {r  parallel, cache=FALSE}
require(snowfall) 
sfInit(parallel=TRUE, cpu=16)
````

``` {r sdp_mat}
SDP_Mat1 <- SDP_by_simulation(f, pars1, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
````

@@

``` {r sdp_mat2}
SDP_Mat2 <- SDP_by_simulation(f, pars2, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
````

@@

``` {r sdp_mat3}
SDP_Mat3 <- SDP_by_simulation(f, pars3, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
````
